---
title: "Bayesian Inference with a Normal Likelihood"
output: html_notebook
---

In this simulation we're going to:
- Generate instances of a random variable with a normal distribution.
- Plot a normal-scaled inverse gamma distribution (the conjugate prior to the normal distribution).
- Plot a normal likelihood surface.
- Plot the posterior using the closed-form solution.
- Plot the posterior predictive (which is yet another normal-scaled inverse gamma distribution).

I'm curious to see what the normal-scaled inverse gamma distribution looks like. I think it would be a good idea to extract the maximum a posteriori estimates (i.e the mode of the posteior) and the maximum likelihood estimates for the mean and variance.

```{r, echo = FALSE}
library(plot3D)
set.seed(1)
n_observations <- 20
true_mean      <- 50
true_sd        <- 5
observations   <- rnorm(n = n_observations, mean = true_mean, sd = true_sd)

sd_grid         <- seq(0.01, 8, 0.25)
mean_grid       <- seq(45, 55, 0.5)
likelihood_surf <- sapply(sd_grid, 
                         function(sd) { # Each column corresponds to a mean value
                           sapply(mean_grid,
                                 function(mu) {
                                   prod(sapply(observations,
                                          function(x) {
                                             dnorm(x, mu, sd)
                                           }))
                                 })
                           })
persp3D(mean_grid, sd_grid, likelihood_surf,
        zlim = c(-5*max(likelihood_surf), max(likelihood_surf)), 
        contour = TRUE, col = 'white',
        border = 'blue', main = 'Likelihood',
        xlab = 'Mean', ylab = 'SD', zlab = 'Density', expand = 1,
        d = 5)

```
```{r, echo = FALSE}
NormInvGam <- function(mu, sd, alpha, beta, gamma, delta) {
                (
                (sqrt(gamma)/sd*sqrt(2*pi)) *
                (beta^alpha / gamma(alpha)) *
                (1/sd^2)^(alpha + 1) *
                exp(-(2*beta + gamma*(delta - mu)^2) / (2*sd^2))
                )
              }

prior_params <- c(0.1, 10, 5, 50)
prior_surf   <- sapply(sd_grid, 
                         function(sd) { # Each column corresponds to a mean value
                           sapply(mean_grid,
                                 function(mu) NormInvGam(mu, sd, prior_params[1],
                                                         prior_params[2], prior_params[3], prior_params[4]))
                                 }
                         )
persp3D(mean_grid, sd_grid, prior_surf,
        zlim = c(0, max(prior_surf)), 
        contour = FALSE, col = 'white',
        border = 'blue', main = 'Prior',
        xlab = 'Mean', ylab = 'SD', zlab = 'Density',
        ticktype = 'detailed', shade = FALSE, expand = 0.5, d = 5)

```


```{r, echo = FALSE}
# Calculate the posterior
post_params    <- prior_params
post_params[1] <- prior_params[1] + n_observations/2
post_params[3] <- prior_params[3] + n_observations
post_params[4] <- (prior_params[3]*prior_params[4] + sum(observations))/(prior_params[3] + n_observations)
post_params[2] <- ((sum(sapply(observations, function(t) t^2))/2) 
                    + prior_params[2] + ((prior_params[3]*prior_params[4]^2)/2)
                      - ((prior_params[3]*prior_params[4] + sum(observations))^2 / (2*(prior_params[3] + n_observations))))

post_surf      <- sapply(sd_grid, 
                         function(sd) { # Each column corresponds to a mean value
                           sapply(mean_grid,
                                 function(mu) NormInvGam(mu, sd, post_params[1],
                                                         post_params[2], post_params[3], post_params[4]))
                                 }
                         )

persp3D(mean_grid, sd_grid, post_surf,
        zlim = c(0, max(post_surf)), 
        contour = FALSE, col = 'white',
        border = 'blue', main = 'Posterior',
        xlab = 'Mean', ylab = 'SD', zlab = 'Density',
        ticktype = 'detailed', shade = FALSE, expand = 0.5, d = 5)
```